The yaq Project: \\ A Standard for Scientific Instrumentation

### 2022-10-31 paper.tex
fix textit

In this section we describe the architecture of the \yaq{} framework in light of three major barriers that we have encountered in scientific instrumentation development.
\textit{First barrier: Multiple interfaces are used to communicate with each component of the system.}
A fully automated system must be able to use all of these interfaces, a daunting task for scientists who do not specialize in software development.
\textit{Second barrier: Coding interfaces adds to a maintenance overhead seldom manageable by researchers.}   Updates to the hardware and operating systems often
require maintenance updates to interfacing code that is not maintainable as researchers are not usually delegated to be strictly software maintainers.
\texit{Third barrier: Certain specialty hardware have inconvenient interface requirements.}
A camera will only work with an obsolete interface card and drivers for Windows XP.
A data acquisition manufacturer provides an Application Programmer Interface (API) that only works in Python 3.7.
A graduate student wishes to drive several stepper motors using a Raspberry Pi.
\texit{Fourth barrier: Some hardware interfaces are blocking.}
A graphical user interface stalls while waiting for a camera to collect data.
Custom orchestration software needs to be closed before the manufacturers configuration software can be used.
A graduate student finds themself needing to master advanced concepts in concurrency in order to orchestrate many motors performantly.

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/network2}
\caption{\label{fig:network2} Networking diagram}
\end{figure}

>>>>

In this section we describe the architecture of the \yaq{} framework in light of three major barriers that we have encountered in scientific instrumentation development.
\textit{First barrier: Multiple interfaces are used to communicate with each component of the system.}
A fully automated system must be able to use all of these interfaces, a daunting task for scientists who do not specialize in software development.
\textit{Second barrier: Coding interfaces adds to a maintenance overhead seldom manageable by researchers.}   Updates to the hardware and operating systems often
require maintenance updates to interfacing code that is not maintainable as researchers are not usually delegated to be strictly software maintainers.
\textit{Third barrier: Certain specialty hardware have inconvenient interface requirements.}
A camera will only work with an obsolete interface card and drivers for Windows XP.
A data acquisition manufacturer provides an Application Programmer Interface (API) that only works in Python 3.7.
A graduate student wishes to drive several stepper motors using a Raspberry Pi.
\textit{Fourth barrier: Some hardware interfaces are blocking.}
A graphical user interface stalls while waiting for a camera to collect data.
Custom orchestration software needs to be closed before the manufacturers configuration software can be used.
A graduate student finds themself needing to master advanced concepts in concurrency in order to orchestrate many motors performantly.

\begin{figure}
	\includegraphics[width=\columnwidth]{figures/network2}
\caption{\label{fig:network} Networking diagram}
\end{figure}
